Starcode: an exact algorithm for sequence clustering

### 2014-07-04 doc/document.tex
Corrected some spelling typos.

Figure~\ref{fig:perf}a shows the running time of starcode as a
function of the number of input sequences $n$. In double logarithmic scale
the trend is a straight line with slope 1.7, which suggests that the
running time complexity of starcode is approximately $O(n^{1.7})$.
Figure~\ref{fig:perf}b shows that the running time gros exponentially
as a function of the maximum Levenshtein distance used for clustering.
This is a common feature of exact algorithms based on trie search. As
this parameter increases, the poucet search bails out at a deeper
average depth in a trie that fans out exponentially.
The running time first increases as a function of the sequence length,
but then plummets and stays low (Figure~\ref{fig:perf}c).
Beyond a certain length, the lookup search algorithm starts to be
efficient, and most of the queries are resolved without the need for
trie-search.
Finally, in we show the scalability of starcode with increasing
number of treahds in Figure~\ref{fig:perf}d. The search algorithm is fully
parallel and the relative performance increases linearly up to 8 threads.
The bending observed thereafter has two sources. The first is 
that the input reading and clustering steps are brief but not parallel,
the second is that there is insufficient memory bandwidth to satisfy
the increased demand of memory accesses and  due to hardware limitations.

>>>>

Figure~\ref{fig:perf}a shows the running time of starcode as a
function of the number of input sequences $n$. In double logarithmic scale
the trend is a straight line with slope 1.7, which suggests that the
running time complexity of starcode is approximately $O(n^{1.7})$.
Figure~\ref{fig:perf}b shows that the running time grows exponentially
as a function of the maximum Levenshtein distance used for clustering.
This is a common feature of exact algorithms based on trie search. As
this parameter increases, the poucet search bails out at a deeper
average depth in a trie that fans out exponentially.
The running time first increases as a function of the sequence length,
but then plummets and stays low (Figure~\ref{fig:perf}c).
Beyond a certain length, the lookup search algorithm starts to be
efficient, and most of the queries are resolved without the need for
trie-search.
Finally, we show the scalability of starcode with increasing
number of treahds in Figure~\ref{fig:perf}d. The search algorithm is fully
parallel and the relative performance increases linearly up to 8 threads.
The bending observed thereafter has two sources. The first is 
that the input reading and clustering steps are brief but not parallel,
the second is due to hardware limitations, i.e. there is insufficient
memory bandwidth to satisfy the increased demand of memory accesses.
